BOLD Parameter Estimation Using Particle Filters

### 2010-12-13 doc/thesis/results.tex
updated thesis for first ETD

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge}
\caption[\acs{BOLD} estimate converging for a very long \acs{fMRI} run.]{\acs{BOLD} estimate 
converging for a 2400 second \acs{fMRI} run. Darker bars indicate
bins with more particles with \acs{BOLD} estimate in that range. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:long_converge}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge_500}
\caption[First 500 seconds of the \acs{BOLD} estimate converging for a very 
long \acs{fMRI} run.]{First 500 seconds of \acs{BOLD} estimate 
converging for a 2400 second \acs{fMRI} run. Darker bars indicate
bins with more particles with \acs{BOLD} estimate in that range. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:long_converge_500}
\end{figure}

@@

%LOW NOISE SECTION, with a signal
\subsection{Simulation with Low Noise}
\label{sec:SimLowNoise}
%tests had noise of $ \{\sigma_y = .01, \sigma_x = .005\} $, where $\sigma_y$ is the
%measurement noise, and $\sigma_x$ is the wiener step size. Both signals used the
%parameters .
%The particle filter used the parameters defined in \autoref{tab:Prior} (\autoref{sec:PriorDistrib}),
%thus the particle filter was not centered over the correct values.
\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/realization_lownoise}
\caption[Simulated Signal with Low Noise/Drift]
{Simulated signals with different noise realizations compared to true
signal. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:LowNoiseRealization}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_lownoise}
\caption[Preprocessed Signal with Low Noise/Drift]
{Results of preprocessing compared to the true signal. 
 Knots of spline placed every 20 measurements.
 ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:PreprocessedLowNoise}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_lownoise}
\caption[Results with Low Noise/Drift]
{Results of the particles filter with preprocessed signals from \autoref{fig:PreprocessedLowNoise}
as input.}
\label{fig:FitComparisonLowNoise}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \acs{RMSR} & \acs{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 & 5.1019 &  0.003211  & 0.00224\\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 & 5.1187 &  0.003055  & 0.00223\\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 & 5.1672 &  0.003289  & 0.00205\\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 & 5.0439 &  0.002847  & 0.00147\\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 & 5.0240 &  0.003006  & 0.00213\\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 & 5.0553 &  0.002833  & 0.00184\\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 & 4.9968 &  0.003028  & 0.00255\\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 & 5.1265 &  0.003044  & 0.00238\\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 & 4.9909 &  0.003345  & 0.0027 \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 & 5.0330 &  0.003175  & 0.00244\\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 & 5.0735 &  0.002889  & 0.00188\\
\hline                                                                               
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 & 5.0665 & 0.003066     & 0.00217\\
\hline
\end{tabular}
\caption[Estimated Parameters with low noise.]
{Estimated Parameters on 11 different runs with low noise. First row is the true value, 
last is the average. $\sum \tau$ is the sum of the estimated time constants.}
\label{tab:LowNoiseResults}
\end{table}

@@

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_highnoise}
\caption[Preprocessed Signal with High Noise/Drift]
{Results of preprocessing compared to the true signal.  
 Knots of spline placed every 20 measurements. ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{fig:PreprocessedHighNoise}
\end{figure}

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_highnoise}
\caption[Results with High Noise/Drift]
{Results of the particles filter with preprocessed signals from \autoref{fig:PreprocessedHighNoise}
as input.}
\label{fig:FitComparisonHighNoise}
\end{figure}

@@

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \acs{RMSR} & \acs{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.1900 & 0.2349 & 0.4223 & 0.128  & 1.0147 & 2.4779 & 1.1168 & 4.6826 &0.01406 & 0.00859\\
0.9721 & 0.2190 & 0.3051 & 0.061  & 0.5780 & 1.9960 & 3.4613 & 3.5461 &0.01373 & 0.00735\\
1.5795 & 0.1415 & 0.3380 & 0.1089 & 0.5843 & 2.1247 & 1.7834 & 4.2885 &0.01275 & 0.00951\\
1.1094 & 0.2374 & 0.5349 & 0.0351 & 1.2186 & 3.0736 & 2.3504 & 5.4016 &0.01673 & 0.00479 \\
1.1071 & 0.2753 & 0.3365 & 0.0316 & 1.5057 & 2.6518 & 4.1910 & 5.2646 &0.01370 & 0.00475\\
0.5803 & 0.4793 & 0.4135 & 0.1189 & 0.9756 & 3.6902 & 1.0008 & 5.2461 &0.01150 & 0.00672\\
\rowcolor[rgb]{.9,.5,.5}
1.2952 & 0.2596 & 0.2756 & 0.2595 & 1.7026 & 2.8458 & 0.6617 & 5.8436 &0.01555 & 0.01039\\
\rowcolor[rgb]{.5,.5,.9}
1.5185 & 0.2199 & 0.2835 & 0.0742 & 0.8882 & 3.0771 & 1.7393 & 5.4838 &0.01205 & 0.00655\\
0.6874 & 0.3283 & 0.3979 & 0.1561 & 1.0778 & 3.1158 & 0.6643 & 4.8810 &0.01510 & 0.0057 \\
1.0170 & 0.285  & 0.3474 & 0.0567 & 1.5877 & 2.6516 & 2.2852 & 5.2563 &0.01249 & 0.00582\\
0.9925 & 0.298  & 0.3221 & 0.2094 & 0.4276 & 2.2108 & 1.0167 & 3.6308 &0.01217 & 0.00916\\
\hline
1.0954 & 0.2708 & 0.3615 & 0.1126 & 1.0510 & 2.7196 & 1.8428 & 4.8659 &0.01362 & 0.00721\\
\hline
\end{tabular}
\caption[Estimated Parameters on 11 different runs with high noise.]
{Estimated Parameters on 11 different runs with high noise. First row contains the true parameters,
last row contains the mean.
The red row is Run 1 and the blue row is Run 2 from  \autoref{fig:NoiseComparisonJustTwo}
and \autoref{fig:FitComparisonHighNoiseJust2}, respectively.}
\label{tab:HighNoiseResults}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 6cm 3.5cm,width=15cm]{images/preprocessed_noiseonly}
\caption[Preprocessed Signal for non-active, low noise signal]
{Comparison of the preprocessed signals for the low noise signal-free case.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{fig:PreprocessedNoiseOnly}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/fits_noiseonly}
\caption[Results for non-active, low noise signal]  
{Comparison of the estimated \ac{BOLD} signal for the low noise signal-free case.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$). Note the line thickness is caused
by all the estimates overlapping.}
\label{fig:fits_noiseonly}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & \acs{RMSR} \\
\hline
1.0324 & 0.33211 & 0.34058 & 0.03012 & 1.40665 & 2.52079 & 0.5311 &   0.00167  \\
 0.98189 & 0.33047 & 0.3386 & 0.03014 & 1.45707 & 2.47232 & 0.45049 & 0.00159   \\
 1.0429 & 0.33224 & 0.34124 & 0.02946 & 1.4618 & 2.49245 & 0.43012 &  0.00165   \\
 1.02054 & 0.3321 & 0.33484 & 0.02586 & 1.45848 & 2.48741 & 0.4193 &  0.00151   \\
 1.0565 & 0.33405 & 0.33758 & 0.02791 & 1.43784 & 2.52545 & 0.47517 & 0.00152   \\
 1.01867 & 0.33528 & 0.33918 & 0.02782 & 1.48345 & 2.49605 & 0.44209 &0.00156   \\
 1.051 & 0.33038 & 0.33837 & 0.02985 & 1.47651 & 2.48621 & 0.42719 &  0.00159   \\
 1.00281 & 0.32929 & 0.33988 & 0.0298 & 1.43519 & 2.49256 & 0.48899 & 0.00164   \\
 1.00893 & 0.33273 & 0.33982 & 0.0289 & 1.42903 & 2.49754 & 0.45688 & 0.00168   \\
 1.01289 & 0.33275 & 0.3376 & 0.02997 & 1.41188 & 2.49881 & 0.50628 & 0.00183   \\
 1.10247 & 0.33371 & 0.3419 & 0.02939 & 1.43774 & 2.53384 & 0.44079 & 0.00195   \\
\hline
1.03009 & 0.33228 & 0.33905 & 0.02902 & 1.44506 & 2.50031 & 0.46076 & 0.00165 \\
\hline
\end{tabular}
\caption[Estimated Parameters with low noies, and no signal.]
{Estimated Parameters on 11 different runs with low noise and no signal present.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{tab:NoiseOnlyResults}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justnoise_fit_0}
\caption[Single Fit Results for non-active, low noise signal.]
{Single Fit Results for non-active, low noise signal
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$).}
\label{fig:justnoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

@@

\begin{figure}[H]
\centering
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/justnoise_hist_3}}
\caption[Convergence of the parameters during a noise-only run.]
{Convergence of the parameters when the signal consisted purely of low level noise 
($\sigma_x = 0.01$, $\sigma_y = 0.005$).
Order of estimates: $\tau_0, \alpha, E_0, V_0, \tau_s, \tau_f, \epsilon, v,
q, s, f, BOLD$.  The bars represent
a histogram, where darker bars indicate more particles with parameters in that bin. The red 
line is the parameter used to generate the true signal, blue line is the final mean of the
particles. See \autoref{fig:justnoise_fit_0}}
\label{fig:JustNoiseConvergence}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3cm,width=15cm]{images/fits_noiseonly_high}
\caption[Results for non-active, high noise signal.]
{\ac{BOLD} estimates for the non-active, high noise signal ($\sigma_x = 0.1$, $\sigma_y = 0.05$). 
Note the line thickness is caused by all the estimates overlapping.}
\label{fig:fits_noiseonly_high}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justbignoise_fit_0}
\caption[Single Fit Results for non-active, high noise signal.]
{Single Fit Results for non-active, high noise signal
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$).}
\label{fig:justbignoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

@@

\caption[Comparison of activation regions.]
{Comparison of activation regions, a) grey matter and regions, b) \acs{SNR} of active
regions, c) \acs{RMSR} Map, d) \acs{MI} Map.}
\label{fig:simslice_hm}
\end{figure}

@@

\begin{figure} %bottom left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=\textwidth]{images/slicesim_hist1}
\caption[Histogram of estimated parameters in section 1]{Histogram of estimated parameters in 
section 1 in voxels 
with \acs{MI} greater than $0.15$} \label{fig:slicesim_hist1}
\end{figure}

\begin{figure} %top left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=\textwidth]{images/slicesim_hist2}
\caption[Histogram of estimated parameters in section 2]
{Histogram of estimated parameters in section 2 in voxels with \acs{MI} greater
than $0.15$}
\label{fig:slicesim_hist2}
\end{figure}

\begin{figure} %top right
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=\textwidth]{images/slicesim_hist3}
\caption[Histogram of estimated parameters in section 3]
{Histogram of estimated parameters in section 3 in voxels with \acs{MI} greater
than $0.15$}
\label{fig:slicesim_hist3}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge}
\caption[\acs{BOLD} estimate 
converging for a 2400 second \acs{fMRI} run.]{\acs{BOLD} estimate 
converging for a 2400 second \acs{fMRI} run. Darker bars indicate
bins with more particles with \acs{BOLD} estimate in that range. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:long_converge}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge_500}
\caption[First 500 seconds of \acs{BOLD} estimate 
converging for a 2400 second \acs{fMRI} run.]{First 500 seconds of \acs{BOLD} estimate 
converging for a 2400 second \acs{fMRI} run. Darker bars indicate
bins with more particles with \acs{BOLD} estimate in that range. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:long_converge_500}
\end{figure}

@@

%LOW NOISE SECTION, with a signal
\subsection{Simulation with Low Noise}
\label{sec:SimLowNoise}
%tests had noise of $ \{\sigma_y = .01, \sigma_x = .005\} $, where $\sigma_y$ is the
%measurement noise, and $\sigma_x$ is the wiener step size. Both signals used the
%parameters .
%The particle filter used the parameters defined in \autoref{tab:Prior} (\autoref{sec:PriorDistrib}),
%thus the particle filter was not centered over the correct values.
\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/realization_lownoise}
\caption[Simulated signals with different noise realizations compared to true
signal.] {Simulated signals with different noise realizations compared to true
signal. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:LowNoiseRealization}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_lownoise}
\caption[Results of preprocessing compared to the true signal.]
{Results of preprocessing compared to the true signal. 
 Knots of spline placed every 20 measurements.
 ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:PreprocessedLowNoise}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_lownoise}
\caption{Results of the particles filter with preprocessed signals from \autoref{fig:PreprocessedLowNoise}
as input.}
\label{fig:FitComparisonLowNoise}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \acs{RMSR} & \acs{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 & 5.1019 &  0.003211  & 0.00224\\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 & 5.1187 &  0.003055  & 0.00223\\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 & 5.1672 &  0.003289  & 0.00205\\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 & 5.0439 &  0.002847  & 0.00147\\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 & 5.0240 &  0.003006  & 0.00213\\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 & 5.0553 &  0.002833  & 0.00184\\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 & 4.9968 &  0.003028  & 0.00255\\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 & 5.1265 &  0.003044  & 0.00238\\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 & 4.9909 &  0.003345  & 0.0027 \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 & 5.0330 &  0.003175  & 0.00244\\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 & 5.0735 &  0.002889  & 0.00188\\
\hline                                                                               
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 & 5.0665 & 0.003066     & 0.00217\\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise. First row is the true value, 
last is the average. $\sum \tau$ is the sum of the estimated time constants.}
\label{tab:LowNoiseResults}
\end{table}

@@

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_highnoise}
\caption[Results of preprocessing compared to the true signal.]
{Results of preprocessing compared to the true signal.  
 Knots of spline placed every 20 measurements. ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{fig:PreprocessedHighNoise}
\end{figure}

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_highnoise}
\caption{Results of the particles filter with preprocessed signals from \autoref{fig:PreprocessedHighNoise}
as input.}
\label{fig:FitComparisonHighNoise}
\end{figure}

@@

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \acs{RMSR} & \acs{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.1900 & 0.2349 & 0.4223 & 0.128  & 1.0147 & 2.4779 & 1.1168 & 4.6826 &0.01406 & 0.00859\\
0.9721 & 0.2190 & 0.3051 & 0.061  & 0.5780 & 1.9960 & 3.4613 & 3.5461 &0.01373 & 0.00735\\
1.5795 & 0.1415 & 0.3380 & 0.1089 & 0.5843 & 2.1247 & 1.7834 & 4.2885 &0.01275 & 0.00951\\
1.1094 & 0.2374 & 0.5349 & 0.0351 & 1.2186 & 3.0736 & 2.3504 & 5.4016 &0.01673 & 0.00479 \\
1.1071 & 0.2753 & 0.3365 & 0.0316 & 1.5057 & 2.6518 & 4.1910 & 5.2646 &0.01370 & 0.00475\\
0.5803 & 0.4793 & 0.4135 & 0.1189 & 0.9756 & 3.6902 & 1.0008 & 5.2461 &0.01150 & 0.00672\\
\rowcolor[rgb]{.9,.5,.5}
1.2952 & 0.2596 & 0.2756 & 0.2595 & 1.7026 & 2.8458 & 0.6617 & 5.8436 &0.01555 & 0.01039\\
\rowcolor[rgb]{.5,.5,.9}
1.5185 & 0.2199 & 0.2835 & 0.0742 & 0.8882 & 3.0771 & 1.7393 & 5.4838 &0.01205 & 0.00655\\
0.6874 & 0.3283 & 0.3979 & 0.1561 & 1.0778 & 3.1158 & 0.6643 & 4.8810 &0.01510 & 0.0057 \\
1.0170 & 0.285  & 0.3474 & 0.0567 & 1.5877 & 2.6516 & 2.2852 & 5.2563 &0.01249 & 0.00582\\
0.9925 & 0.298  & 0.3221 & 0.2094 & 0.4276 & 2.2108 & 1.0167 & 3.6308 &0.01217 & 0.00916\\
\hline
1.0954 & 0.2708 & 0.3615 & 0.1126 & 1.0510 & 2.7196 & 1.8428 & 4.8659 &0.01362 & 0.00721\\
\hline
\end{tabular}
\caption[Estimated Parameters on 11 different runs with high noise. First row contains the true parameters,
last row contains the mean.]
{Estimated Parameters on 11 different runs with high noise. First row contains the true parameters,
last row contains the mean.
The red row is Run 1 and the blue row is Run 2 from  \autoref{fig:NoiseComparisonJustTwo}
and \autoref{fig:FitComparisonHighNoiseJust2}, respectively.}
\label{tab:HighNoiseResults}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 6cm 3.5cm,width=15cm]{images/preprocessed_noiseonly}
\caption[Comparison of the preprocessed signals for the low noise signal-free case.
($\sigma_x = 0.005$, $\sigma_y = 0.01$)]
{Comparison of the preprocessed signals for the low noise signal-free case.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{fig:PreprocessedNoiseOnly}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/fits_noiseonly}
\caption[Comparison of the estimated \ac{BOLD} signal for the low noise signal-free case.
($\sigma_x = 0.005$, $\sigma_y = 0.01$)]  
{Comparison of the estimated \ac{BOLD} signal for the low noise signal-free case.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$). Note the line thickness is caused
by all the estimates overlapping.}
\label{fig:fits_noiseonly}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & \acs{RMSR} \\
\hline
1.0324 & 0.33211 & 0.34058 & 0.03012 & 1.40665 & 2.52079 & 0.5311 &   0.00167  \\
 0.98189 & 0.33047 & 0.3386 & 0.03014 & 1.45707 & 2.47232 & 0.45049 & 0.00159   \\
 1.0429 & 0.33224 & 0.34124 & 0.02946 & 1.4618 & 2.49245 & 0.43012 &  0.00165   \\
 1.02054 & 0.3321 & 0.33484 & 0.02586 & 1.45848 & 2.48741 & 0.4193 &  0.00151   \\
 1.0565 & 0.33405 & 0.33758 & 0.02791 & 1.43784 & 2.52545 & 0.47517 & 0.00152   \\
 1.01867 & 0.33528 & 0.33918 & 0.02782 & 1.48345 & 2.49605 & 0.44209 &0.00156   \\
 1.051 & 0.33038 & 0.33837 & 0.02985 & 1.47651 & 2.48621 & 0.42719 &  0.00159   \\
 1.00281 & 0.32929 & 0.33988 & 0.0298 & 1.43519 & 2.49256 & 0.48899 & 0.00164   \\
 1.00893 & 0.33273 & 0.33982 & 0.0289 & 1.42903 & 2.49754 & 0.45688 & 0.00168   \\
 1.01289 & 0.33275 & 0.3376 & 0.02997 & 1.41188 & 2.49881 & 0.50628 & 0.00183   \\
 1.10247 & 0.33371 & 0.3419 & 0.02939 & 1.43774 & 2.53384 & 0.44079 & 0.00195   \\
\hline
1.03009 & 0.33228 & 0.33905 & 0.02902 & 1.44506 & 2.50031 & 0.46076 & 0.00165 \\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise and no signal present.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{tab:NoiseOnlyResults}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justnoise_fit_0}
\caption {Single Fit Results for non-active, low noise signal ($\sigma_x = 0.005$, $\sigma_y = 0.01$).}
\label{fig:justnoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

@@

\begin{figure}[H]
\centering
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/justnoise_hist_3}}
\caption[Convergence of the parameters when the signal consisted purely of low level noise 
($\sigma_x = 0.01$, $\sigma_y = 0.005$).]
{Convergence of the parameters when the signal consisted purely of low level noise 
($\sigma_x = 0.01$, $\sigma_y = 0.005$).
Order of estimates: $\tau_0, \alpha, E_0, V_0, \tau_s, \tau_f, \epsilon, v,
q, s, f, BOLD$.  The bars represent
a histogram, where darker bars indicate more particles with parameters in that bin. The red 
line is the parameter used to generate the true signal, blue line is the final mean of the
particles. See \autoref{fig:justnoise_fit_0}}
\label{fig:JustNoiseConvergence}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3cm,width=15cm]{images/fits_noiseonly_high}
\caption[\ac{BOLD} estimates for the non-active, high noise signal ($\sigma_x = 0.1$, $\sigma_y = 0.05$).]
{\ac{BOLD} estimates for the non-active, high noise signal ($\sigma_x = 0.1$, $\sigma_y = 0.05$). 
Note the line thickness is caused by all the estimates overlapping.}
\label{fig:fits_noiseonly_high}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justbignoise_fit_0}
\caption{Single Fit Results for non-active, high noise signal
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$).}
\label{fig:justbignoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

@@

\caption[Comparison of activation regions.]
{Comparison of activation regions. a) grey matter and regions, b) \acs{SNR} of active
regions, c) \acs{RMSR} Map, d) \acs{MI} Map.}
\label{fig:simslice_hm}
\end{figure}

@@

\begin{figure} %bottom left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=\textwidth]{images/slicesim_hist1}
\caption{Histogram of estimated parameters in section 1 in voxels 
with \acs{MI} greater than $0.15$} \label{fig:slicesim_hist1}
\end{figure}

\begin{figure} %top left
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=\textwidth]{images/slicesim_hist2}
\caption
{Histogram of estimated parameters in section 2 in voxels with \acs{MI} greater
than $0.15$}
\label{fig:slicesim_hist2}
\end{figure}

\begin{figure} %top right
\centering
\includegraphics[clip=true,trim=2.5cm 2cm 2cm 1cm,width=\textwidth]{images/slicesim_hist3}
\caption
{Histogram of estimated parameters in section 3 in voxels with \acs{MI} greater
than $0.15$}
\label{fig:slicesim_hist3}
\end{figure}
